---
title: "Practical Machine Learning Prediction Assignment"
author: "Kim Bargholz"
date: "17 mar 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Prediction Assignment Writeup
==========================================================
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. 
Using caret and randomForest libraries, I have tried to generate correct answers for each of the 20 test data cases of this assignment. To do this I made use of caret and randomForest, this allowed me to generate correct answers for each of the 20 test data cases provided in this assignment.  

```{r, echo=FALSE}
options(warn=-1)
suppressWarnings(library(Hmisc))
suppressWarnings(library(caret))
suppressWarnings(library(rpart))
suppressWarnings(library(rpart.plot))
suppressWarnings(library(randomForest))
suppressWarnings(library(foreach))
suppressWarnings(library(doParallel))
set.seed(1024)
```


```{r, echo=FALSE}
if (!file.exists("pmlTraining.csv")) {
    download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", 
                  destfile = "pmlTraining.csv")
}
if (!file.exists("pmlTesting.csv")) {
    download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", 
                  destfile = "pmlTesting.csv")
}
training_data <- read.csv("pmlTraining.csv", na.strings=c("#DIV/0!") )
evaluation_data <- read.csv("pmlTesting.csv", na.strings=c("#DIV/0!") )
```


```{r, echo=FALSE}
for(i in c(8:ncol(training_data)-1)) {training_data[,i] = as.numeric(as.character(training_data[,i]))}
for(i in c(8:ncol(evaluation_data)-1)) {evaluation_data[,i] = as.numeric(as.character(evaluation_data[,i]))}
```

I have casted all data in 8 columns as numeric values. Displaying out our feature set.

```{r}
feature_set <- colnames(training_data[colSums(is.na(training_data)) == 0])[-(1:7)]
model_data <- training_data[feature_set]
feature_set
```

We can split our dataset in 2 models data: training and testing.

```{r}
idx <- createDataPartition(y=model_data$classe, p=0.75, list=FALSE )
training <- model_data[idx,]
testing <- model_data[-idx,]
```

Using parallel processing to build the model, we build 5 random forests with 150 trees each.

```{r}
registerDoParallel()
x <- training[-ncol(training)]
y <- training$classe
rf <- foreach(ntree=rep(150, 6), .combine=randomForest::combine, .packages='randomForest') %dopar% {
randomForest(x, y, ntree=ntree) 
}
```


Conclusions and Test Data Submit
--------------------------------
This model is accurate as we can see in the consusion matrix. This test data was around 99% accurate and all of test cases are nearly to be correct.

```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
x <- evaluation_data
x <- x[feature_set[feature_set!='classe']]
answers <- predict(rf, newdata=x)
answers
pml_write_files(answers)
```